Climate change projected to reduce European life expectancy

### 2018-03-23 MS-cclifeexpec.Rmd
fixed some minor errors. Ready for age-standardized mortality rates.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(png)
rm(list=ls())
library(tidyverse)
library(RColorBrewer)
library(scales)
library(tmap)
library(tmaptools)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(png)
rm(list=ls())
library(tidyverse)
library(HMDHFDplus)
library(LifeTables)
library(xlsx)
library(tmap)
library(tmaptools)
library(RColorBrewer)
library(data.table)
